Open source symbolic multibody dynamics software

### 2012-02-21 PetersonGedeHubbard2012.tex
finished up substition/jacobian part

The computational cost of computing the jacobian matrices can also be reduced
if the point of linearization is known ahead of time.

>>>>

If it is found that substatial computational time is spent in computing the
jacobian matrices, it might be possible to reduce the time if the point of
linearization is known. We are taking the partial derivatives with respect to
$q$, $\dot{q}$, $u$, and $\dot{u}$ in a number of vectors. If we know the point
of linearization (have numerical values for $q$, $\dot{q}$, $u$, $\dot{u}$), we
can substitute all of the quantities except for those we are taking the
derivative with respect to; e.g. when computing $\nabla_{\mb{u}} \bm{f}_3$ we
substitute in the known values for $q$, $\dot{q}$, and $u$. In this situation,
the cost of symbolic substitution needs to be considered. In practice, it has
sometimes been computationally expensive. The potential speed-up needs to be
considered next to the loss of generality of choosing a point of linearization
after the fact.
